\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks = true,
            linkcolor = red,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\hypersetup{pdfborder = 0 0 0}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}

\begin{center}
    {\Huge \scshape Michael Blanchette} \\ \vspace{1pt}
    \small
    \raisebox{-0.1\height}\faPhone\ +852 9421 5885 ~
    \href{mailto:mdblanchette@connect.ust.hk}{\faEnvelope\ mdblanchette@connect.ust.hk} ~ 
    \href{https://www.linkedin.com/in/michaelblanchette/}{\faLinkedin\ -michaelblanchette}  ~
    \href{https://github.com/mdblanchette}{\faGithub\ mdblanchette}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Hong Kong University of Science and Technology}{Sep 2020 -- Jun 2025}
      {Dual Degree Program in Technology \& Management (DDP)}{}
      %leave a line after this
      
      \small{\textbf{BEng Computer Science and BBA Marketing}}
  \resumeSubHeadingListEnd
\vspace{-18pt}

%----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Deloitte}{Jun 2023 -- Aug 2023}
      {Consulting Intern - Digital}{Hong Kong}
      \resumeItemListStart
        \resumeItem {Optimized ServiceNow workflows to develop management and strategic portfolio dashboards for four prominent companies. The solutions were specifically tailored to be used by HR personnel, employees, and customers.}
        \resumeItem {Supervised the quality of Chinese-English translations for ServiceNow portals by translating an average of 200 cells of notifications per day, ensuring high-quality cross-cultural organizational communications.}
        \resumeItem {Compiled meeting minutes involving at least four parties, summarizing and translating key action points and business agreements between five stakeholders engaged in our client’s project.}
%Based on the number of point you want to add add the "\resumeItem" for each point you want to add.
    \resumeItemListEnd
      
    \resumeSubheading
      {Scout Association of Hong Kong (SAHK)}{Sep 2022 -- Present}
      {Instructor}{Hong Kong}
      \resumeItemListStart
        \resumeItem {Attained the Venture Scout Award (VSA) and Chief Scout Award across at least 10 years of scouting.}
        \resumeItem {Leading and coordinating diverse scouting activities for groups of 20 to 40 youths every week.}
        \resumeItem {Mentored and guided over three generations of scout troops, optimizing and facilitating effective leadership councils.}
        \resumeItem{Cultivated our youths’ interest in their scouting journey and maintained an 80\% retention rate of scouts per generation.}
    \resumeItemListEnd

    \resumeSubheading
      {McDonald's Hong Kong}{Jul 2022 - Jun 2023}
      {Youth Consultant}{Hong Kong}
      \resumeItemListStart
        \resumeItem {Established the first committee in McDonald's HK operated entirely by passionate Hong Kong youth.}
        \resumeItem {Partnered with local Hong Kong artists to organize the "Coach McNugget Art World" Exhibition, showcasing over 20 meticulously curated nugget-themed artworks.}
        \resumeItem {Supported the CEO and other board members as a key decision-maker and consultant for McDonald's HK youth-related business decisions.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}
% adjust vscape based on the space you want to leave between each section.

%----------PROJECT EXPERIENCE-----------
\section{Project Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {HKUST TEMG4950L Corporate Consulting Project}{Sep 2023 -- Present}
      {ETF Trading Student Consultant}{Hong Kong}
      \resumeItemListStart
        \resumeItem {Designing a Global ETF Sales Dashboard to aggregate trends from news and social media, progressing JP Morgan’s competitive edge in the ETF trading landscape.}
%Based on the number of point you want to add add the "\resumeItem" for each point you want to add.
    \resumeItemListEnd
    \resumeSubheading
      {HKUST TEMG4940C Corporate Prototyping Project}{Jun 2023 -- Aug 2023}
      {Fixed Income Student Analyst / Full-stack Developer}{Hong Kong}
      \resumeItemListStart
        \resumeItem {Applied machine learning algorithms to data sourced from Eikon Terminal and Yahoo Finance, leading a team to develop a predictive dashboard for corporate sponsors. The dashboard operates on Next.js and Google Cloud Platform to accurately predict changes in bond pricing, achieving 2nd place in the competition.}
        \resumeItem {Identified and utilized 62 features used to predict yearly credit rating migrations with 79.71\% back-tested accuracy.}
        \resumeItem {Developed a yearly credit spread prediction model with an average error of 76.14 basis points.}
%Based on the number of point you want to add add the "\resumeItem" for each point you want to add.
    \resumeItemListEnd
      
    \resumeSubheading
      {Project Melo}{Jan 2022 -- Present}
      {Fellow}{Hong Kong}
      \resumeItemListStart
        \resumeItem {Engaged with prominent Hong Kong CEOs and business leaders to participate in social empowerment initiatives.}
        \resumeItem {Selected as one of 20 fellows from a competitive pool of 200+ applicants and collaborated in a team of 4 with the CEOs of McDonald's HK and Bowtie.}
        \resumeItem {Delivered a TED-style talk at HKUST to an audience of over 500 CEOs from around the world to advocate our initiatives.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------Expertise-----------
\section{Expertise}
 \begin{itemize}[leftmargin=0.1in, label={}]
    \small{\item{
     \textbf{Communication}{: English (Native), Thai (Conversational), Mandarin (Studying), Cantonese (Studying), Spanish (Studying)} \\
     \textbf{Programming}{: Python, Java, C, C\#, C++, HTML, CSS, JavaScript, R, PHP} \\
     \textbf{Technologies}{: React, Next.js, Git, Google Cloud, Agile Development}\\
     \textbf{Tools}{: Adobe Premiere, After Effects, Photoshop, Dreamweaver, iMovie, Autodesk 3DS Max, Autodesk Maya, Blender, SketchUp, AutoCAD, Canva, Figma}\\
     
    }}
 \end{itemize}
 \vspace{-20pt}






\end{document}